A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/conclusion_RECOMB.tex

We must point out that our approach can only detect point wise 
sequencing errors, and only if they are located in base pairs. It 
nonetheless supplements well existing tools by using previously discarded
information.

>>>>

We must recall that our approach is restricted to
 the correction of point-wise error in structured regions (i.e. base paired nucleotides).
 Nonetheless it supplements well existing tools by using previously discarded
information holding, as shown, a strong signal.
